% - - - - - - - - - - - 
% License: MIT
% - - - - - - - - - - - 

\documentclass[12pt]{article}

\title{Resume}
\author{Taylor Neely}

\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\usepackage{ifthen}
\usepackage{titlesec}
\usepackage{enumitem}

% Font & encoding
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\input{glyphtounicode}
\pdfgentounicode=1

% Set layout and margins (H, V)
\geometry{letterpaper, margin={0.5in, 0.5in}}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Clear headers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Format overrides
\titleformat{\section}{\scshape \Large \vspace{-10pt}}{}{0em}{}[\titlerule]

% Commands

\newcommand*{\header}[4]{
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \hspace{-5pt}\textbf{\LARGE{#1}} & \href{mailto:#2}{#2}\\
        \href{#3}{#3} & \href{tel:#4}{#4}
    \end{tabular*}\vspace{-5pt}
}

\newcommand*{\workSectionStart}[1]{\section{#1}\begin{itemize}[label={}, leftmargin=*]}

    \newcommand*{\workItem}[4]{\item
        \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
            \textbf{\large{#1}} & {#2}\\
            \textit{#3} & \textit{#4}
        \end{tabular*}
    }

    \newcommand{\workDataStart}{\begin{itemize}[label=$\circ$]\vspace{-4pt}}
        \newcommand*{\workDataItem}[2][]{\item\ifthenelse{\equal{#1}{}}{}{\textbf{#1:}} #2}
    \newcommand{\workDataEnd}{\end{itemize}}

\newcommand*{\workSectionEnd}{\end{itemize}}

% Whew! All set up now to write the resume below!

\begin{document}

\header
    {Taylor Neely}
    {tneely417@gmail.com}
    {https://tneely.com}
    {734-546-4691}

\workSectionStart{Experience}
    \workItem{Amazon Web Services (AWS)}{Seattle, WA}
        {Senior Software Development Engineer (Health AI)}{Apr. 2021 - Present}
        \workDataStart
            \workDataItem[Service Lead]{Designed and launched AWS HealthOmics, an AWS managed service capable of storing, processing, and
                analyzing petabyte-scale genomics data across 7 AWS regions. Since GA, Taylor has guided and driven the launch of dozens of
                features and service enhancements, expanding the scale of the service by 10x and reducing operational overhead by 80\%.}
            \workDataItem[Cloud Architecture]{Built efficient and scalable cloud-native services, leveraging a serverless, event-driven 
                architecture when possible. This has allowed AWS HealthOmics to scale to support 5,000 RPS over 100 Gbps of bandwidth and
                ingest petabytes of data per day.}
            \workDataItem[Open Source]{Wrote and maintained open source tooling like the Amazon Genomics CLI, an open source tool designed to simplify 
                the process of deploying the AWS infrastructure required to run genomics workflows in the cloud, 
                to submit those workflows to run, and to monitor the logs and outputs of those workflows.}
            \workDataItem[Operational Excellence]{Automated service creation, deployment, and testing to enable our teams to launch AWS
                HealthOmics across new regions in under 10 days and with zero developer overhead. Taylor has also implemented continuous
                integration and delivery tooling via infrastructure as code to support this automation and drive our build, test, release,
                and monitoring processes.}
        \workDataEnd

    \workItem{Amazon}{Seattle, WA}
        {Software Development Engineer (Prime)}{July 2019 - Apr. 2021}
        \workDataStart
            \workDataItem[Customization]{Developed a scalable, low latency, rule-based customization engine to display accurate
                and relevant content to customers across various states in their membership lifecycle. This has been used to drive
                customer aquisition and retention across the Prime organization, supporting over 10 teams and 20 use cases.}
            \workDataItem[Compliance]{Worked across 7 different teams and code bases to idenify gaps in GDPR compliance and address issues in
                functionality prior to enforcement of the law. This has enabled customers to seamlessly and securely authenticate with
                their banks when signing up for Amazon Prime subscriptions.}
            \workDataItem[Cloud Infrastructure]{Identified infrastructure as code as a operational win for Amazon, pioneering and driving
                adoption of CDK across the Prime organization. This has helped teams quickly and repeatedly write and launch
                well-architected services using infrastructure as code for AWS, complete with metrics, alarms, and monitoring dashboards.}
        \workDataEnd

    \workItem{Epic Systems}{Verona, WI}
        {Software Developer}{Aug. 2016 - May 2019}
        \workDataStart
            \workDataItem[Customer Driven]{Worked closely customers to idenify gaps in our software and opportunities for innovation: 
                comprehensive cost estimate tooling for prospective patients, clinically integrated checklists to aid patient readiness and
                reduce surgery delays and cancellations.}
        \workDataEnd
\workSectionEnd

\workSectionStart{Education}
    \workItem{Dartmouth College}{Hanover, NH}
        {Bachelor of Arts in Biology, Computer Science with Honors}{2012 - 2016}
\workSectionEnd

\center{\tiny{\href{https://github.com/tneely/resume}{This resume generated on \today}}
\end{document}
